Digital Addiction

### 2024-02-15 paper/paper.qmd
add abstract

---
title: "Digital Addiction"
subtitle: "Analysis of How Usage of Social Media Impact Objective Well-Being And Political Opinion"
author: 
  - Kenneth Chan, Stephanie Xuan Zhao, Siyu Li
thanks: "Code and data are available at: <https://github.com/YO7O/digital_addiction.git>"
date: today
date-format: long
abstract: "."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Figure 3 
The above figure(@fig-social_life) show whether Facebook usage makes social life worse or better. The x-axis is formed from -6 to 6 which is based on a set of marking schemes for the research target to scale. From the figure, it has changed between -1 and 1. At baseline, it has the most fraction at 0 for the treatment group and in the control group, it has the most in -1 and 0. However, in endline’s figure, the biggest fraction shifts to the right. It becomes 0 and 1. This means that user feels their social life becomes better. This helps to prove that with less time spent on Facebook, people’s objective well-being increases.

@@

This two graphs(@fig-political_opinion_1)(@fig-political_opinion_2) shows whether people change their political stance when using Facebook or not. The two different political positions are Republican, Democrat or Independent and Liberal or Conservative. obviously, we can see from the Republican graph that most people would still strongly choose Strongly Democratic, almost to 0.3 The distance is almost 0.3. In the Liberal graph, we can see that most people would choose liberal over extremely liberal, with a figure of more than 0.3.

>>>>

---
title: "Digital Addiction"
subtitle: "Analysis of How Usage of Social Media Impact Objective Well-Being And Political Opinion"
author: 
  - Kenneth Chan, Stephanie Xuan Zhao, Siyu Li
thanks: "Code and data are available at: <https://github.com/YO7O/digital_addiction.git>"
date: today
date-format: long
abstract: "The global population of social media users is predicted to reach 4.95 billion by 2023; this is a significant increase from the 2.05 billion users in 2015 (source: Backlinko). As technology continues to evolve, smartphones are playing an increasingly important role in our daily lives, providing us with more and more services. However, the impact of smartphones on our lives still needs to be further explored. In this paper, we will discuss two aspects. First, we explore the impact of the social media Facebook on social and political attitudes, providing insights and calling for further research on interventions to mitigate its negative effects. The paper analyzes experimental data related to subjective well-being by experimentally surveying participants and using an analytic factorial design to randomize them into reward and restriction groups. The study uses regression modelling to assess the impact of specific digital technology use patterns on well-being. We also examine whether Facebook use affects people's political attitudes."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

The above figure(@fig-social_life) show whether Facebook usage makes social life worse or better. The x-axis is formed from -6 to 6 which is based on a set of marking schemes for the research target to scale. From the figure, it has changed between -1 and 1. At baseline, it has the most fraction at 0 for the treatment group and in the control group, it has the most in -1 and 0. However, in endline’s figure, the biggest fraction shifts to the right. It becomes 0 and 1. This means that user feels their social life becomes better. This helps to prove that with less time spent on Facebook, people’s objective well-being increases.

@@

This graphs(@fig-political_opinion_1)(@fig-political_opinion_2) shows whether people change their political stance when using Facebook or not. The two different political positions are Republican, Democrat or Independent and Liberal or Conservative. obviously, we can see from the Republican graph that most people would still strongly choose Strongly Democratic, almost to 0.3 The distance is almost 0.3. In the Liberal graph, we can see that most people would choose liberal over extremely liberal, with a figure of more than 0.3. So from this graph social media affects a lot of people who are liberal and conservatives are in the minority.
